---
title: "ETO5513-A1"
author: "Eileen Koh"
date: "2026-03-15"
output:
  bookdown::html_document2:
    keep_md: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
knitr::opts_chunk$set(fig.path = "Figures", fig.align ="center", out.width = "50%")
#options(bookdown.table.caption = FALSE)
```

# Part A

## Section 1: Load libraries


```{r load libraries, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,   warning = FALSE,
  message = FALSE)

library(knitr)
library(markdown)
library(tidyverse)
library(readxl)
library(ggplot2)  #Plots
library(dplyr)
library(bookdown)
library(kableExtra)
```

## Section 2: Research questions

1. What are the life expectancy and life satisfaction in Asia countries? 
2. Is life expectancy correlated with life satisfaction?



## Section 3: Data set introduction


This dataset from Our World in Data website ["Life satisfaction vs. life expectancy"] (https://ourworldindata.org/grapher/life-satisfaction-vs-life-expectancy)  shows the life expectancies at birth, population size and self-reported life satisfaction across countries from 2011 to 2024. The dataset has been reduced to include only selected Asia countries. 

For self-reported life satisfaction, the respondents are supposed to think of a ladder, with the best possible life for them being a 10 and the worst possible life being a 0. They are then asked to rate their own current lives on that 0 to 10 scale.

### Exploring dataset


```{r data}
life_df <- readxl::read_excel("C:/Users/eleen/Documents/Documents/Monash Units/TP2-26_ETO5513 Collaborative/A1/ETO5513-A1/Data/Life Expectancy and Life Satisfaction_Asia.xlsx")
```

```{r Explore data}
head(life_df)
glimpse(life_df)
summary(life_df)
# use kable to report variables
```

### Table 1: List of variables in dataset {#refTable1}

```{r var-table}
knitr::kable(
  data.frame(Variable = names(life_df)),
  caption = "List of variables in the dataset"
)
```


As shown in Table \@ref(tab:var-table), the dataset contains several variables.


## Declaration

I acknowledge the use of ChatGPT (https://chat.openai.com/) to debug errors in code and enhancing language or grammar.

