---
title: "ETO5513-A1"
author: "Eileen Koh"
date: "2026-03-15"
output: html_document
---


# Part A

## Section 1: Load libraries


```{r libraries, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,   warning = FALSE,
  message = FALSE)

library(knitr)
library(markdown)
library(tidyverse)
library(readxl)
library(ggplot2)  #Plots
library(dplyr)
library(bookdown)

```

## Section 2: Research questions

1. What are the life expectancy and life satisfaction in Asia countries? 
2. Is life expectancy correlated with life satisfaction?



## Section 3: Data set introduction

This dataset shows the life expectancies at birth, population size and self-reported life satisfaction across Asia countries from 2011 to 2024. For self-reported life satisfaction, the respondents are supposed to think of a ladder, with 
the best possible life for them being a 10 and the worst possible life being a 0. They are then asked to rate their own current lives on that 0 to 10 scale.



```{r data}
life_df <- readxl::read_excel("C:/Users/eleen/Documents/Documents/Monash Units/TP2-26_ETO5513 Collaborative/A1/ETO5513-A1/Data/Life Expectancy and Life Satisfaction_Asia.xlsx")
```

```{r Explore data}
head(life_df)
glimpse(life_df)
summary(life_df)
# use kable to report variables

kable(
  data.frame(Variable = names(life_df)),
  caption = "List of variables in the dataset"
)
```

